### 2011-09-02 docs/architecture/architecture.tex
update directory structure -- still need to do the graphic

\maestro\ can use adaptive mesh refinement to focus resolution on
complex regions of flow.  For Cartesian/plane-parallel geometries, all
cells at the same height must be at the same level of refinement.
This restriction is to allow for the base state to directly align with
the Cartesian state everywhere.  For spherical geometries, there is no
such restriction (again, see Figure~\ref{fig:base_state}).

@@

All the files needed to build \maestro\ are contained in the {\tt
  fParallel} directory structure.  Problems piece together various
\maestro\ directories, choosing a reaction network, equation of state,
and conductivity routine to build an executable.  Briefly, the
sub-directories are:
\begin{itemize}
\item {\tt boxlib/}

 BoxLib is a library for describing meshes consisting of a union
 of boxes.  The BoxLib modules define the basic datatypes used
 in \maestro.  BoxLib also provides the routines that handle the
 parallelization and I/O.

\item {\tt data\_processing/}

@@

 Important sub-directories include:
 \begin{itemize}
 \item {\tt conductivity/}

@@

\item {\tt mg/}

  The multigrid solver, with support for both cell-centered and
  node-centered data.

\item {\tt mk/}

@@

\item {\tt scripts/}

>>>>

\maestro\ can use adaptive mesh refinement to focus resolution on
complex regions of flow.  For Cartesian/plane-parallel geometries, all
cells at the same height must be at the same level of refinement.
This restriction is to allow for the base state to directly align with
the Cartesian state everywhere.  For spherical geometries, there is no
such restriction (again, see Figure~\ref{fig:base_state}).
The \maestro\ grids are managed by the \boxlib\ library, which is
distributed separately.

@@

Building \maestro\ requires both the \maestro-specific source
files (distributed in the {\tt MAESTRO/} directory), and the
\boxlib\ library (distributed in the {\tt BoxLib/} directory.
\boxlib\ provides both a C++ and a Fortran framework.  \maestro\
only uses the Fortran framework.

Problems piece together various \maestro\ directories, choosing a
reaction network, equation of state, and conductivity routine to build
an executable.  Briefly, the \maestro\ sub-directories are:
\begin{itemize}
\item {\tt data\_processing/}

@@

  Important sub-directories include:

  \begin{itemize}
  \item {\tt conductivity/}

@@

The \boxlib\ directories that \maestro\ uses are:
\begin{itemize}
\item {Src/}

  The main \boxlib\ source directory.  In \maestro, we only use the
  Fortran source files.  The core directories are:

  \item {\tt F\_BaseLib/}

    The Fortran \boxlib\ files.  This is a library for describing
    meshes consisting of a union of boxes.  The \boxlib\ modules
    define the basic datatypes used in \maestro.  \boxlib\ also
    provides the routines that handle the parallelization and I/O.

  \item {\tt LinearSolvers/}

    The \boxlib\ linear solvers---these are used to solve elliptic
    problems in the \maestro\ algorithm.

    \item {\tt F\_MG}

      The Fortran multigrid solver, with support for both
      cell-centered and node-centered data.

\item {\tt Tools/}

  Various tools used for building \boxlib\ applications.  Here we use:

  \item {F\_mk/}

@@

  \item {\tt F\_scripts/}
